---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# symmoments

<!-- badges: start -->
[![R-CMD-check](https://github.com/FloSchuberth/symmoments/actions/workflows/rhub.yaml/badge.svg)](https://github.com/FloSchuberth/symmoments/actions)
<!-- badges: end -->

The symmoments R package can be used to Symbolically compute and numerically evaluate multivariate normal moments \eqn{E[X_1^{k_1} \cdots X_n^{k_n}]}, where \eqn{(X_1,\ldots,X_n) \sim N(\mu, \Sigma)}, in terms of mu and S elements.

## Installation

You can install the development version of symmoments from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("FloSchuberth/symmoments")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(symmoments)
 # Compute the moment for the 4-dimensional moment c(1,2,3,4):
callmultmoments(c(1,2,3,4))

# Print the representation of the 4-dimensional moment c(1,2,3,4):
print(callmultmoments(c(1,2,3,4)))

# Compute the LaTeX representation of the central moment c(1,2,3,4):
toLatex(callmultmoments(c(1,2,3,4)))

# evaluate the moment c(1,2,3,4) at the following variance-covariance matrix
#  4 2 1 1
#  2 3 1 1
#  1 1 2 1
evaluate(callmultmoments(c(1,2,3,4)), c(4,2,1,1,3,1,1,2,1,2))
```


